About p-adic stability in linear algebra

### 2014-12-19 examples/stability.tex
Added bibliography on (sub)resultants
Extended version of abstract :-)
Small fixes

\begin{abstract}
Based on the framework developed in \cite{caruso-roe-vaccon:14a}, we study 
the $p$-adic stability of standard operations on matrices and vector 
spaces. 
%We observe in particular that generic algorithms --- which are 
%designed to work over an arbitrary field --- are generally very 
%unstable.
\end{abstract}

@@

\begin{prop}
\label{prop:mulmatrix}
With the above notations, we have:
$$\begin{array}{rl}
& \mathcal P'_{a,b,c}(A,B)(\mathcal L_0)
= U_A \cdot M_{r,t}((a_i),(b_j)) \cdot V_B \smallskip \\
\text{and} &
\displaystyle 
[\mathcal P'_{a,b,c}(A,B)(\mathcal L_0) : M_{r,t}(\O_K)] =
\sum_{m=1}^\infty a^{(m)} b^{(m)}
\end{array}$$
where $a^{(m)}$ (resp. $b^{(m)}$) is the number of $a_i$'s (resp.
of $b_j$'s) which are $\geq m$.
\end{prop}

>>>>

\begin{abstract}
Based on the framework of ``differential precision'' developed in a
previous work by the same authors, we study 
the $p$-adic stability of standard operations on matrices and vector 
spaces. In particular, we highlight that lattice-based methods can be
quite profitable in many cases (\emph{e.g.} matrix multiplication). We 
underpin this observation by numerous numerical evidences.
\end{abstract}

@@

\begin{prop}
\label{prop:mulmatrix}
With the above notations, we have:
$$\begin{array}{rl}
& \mathcal P'_{a,b,c}(A,B)(\mathcal L_0)
= U_A \cdot M_{r,t}((a_i),(b_j)) \cdot V_B \smallskip \\
\text{and} &
\text{\emph{length}}\Big(\frac{\mathcal P'_{a,b,c}(A,B)(\mathcal L_0) }
{M_{r,t}(\O_K)}\Big) =
\displaystyle 
\sum_{m=1}^\infty a^{(m)} b^{(m)}
\end{array}$$
where $a^{(m)}$ (resp. $b^{(m)}$) is the number of $a_i$'s (resp.
of $b_j$'s) which are $\geq m$.
\end{prop}
